Carbonate chemistry at Ny-Ålesund

### 2021-11-08 awipev-CO2.Rmd

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")

>>>>

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
